---
title: "Data Repositories"
output:
  html_document:
    toc: false
    toc_float:
      collapsed: false
    includes:
      before_body: [includes/include_header.html, includes/include_header_navpage.html]
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```


<link href="https://use.fontawesome.com/releases/v5.0.6/css/all.css" rel="stylesheet">

## Data Repositories

Data repositories are dedicated tools for depositing research data such that it can be easily accessed and cited by others, via a dedicated DOI (digital object identifier). Researchers are highly recommended to always deposit data in a dedicated repository instead of as "supplementary materials" alongside publications, for two very important reasons:

- Your data and publication are unique outputs, they should be uniquely and separately citable
- Your data and publications have completely different meta data to one another, for instance: file formats, file size, encoding etc.

Fortunately, it is typically free and very easy to deposit into a data repository. There are essentially two different types of repository:

<hr>

<div class='row'>

<div class='col-sm-6'>

<center><h5>General Purpose Repositories</h5></center>
<center><i class='fas fa-archive fa-2x'></i></center>
These repositories will accept a wide range of file formats and typically have a small number of meta-data fields for deposits to try and make the descriptors as general purpose as possible. **OxShef: Publishers** maintains an overview of the most popular general purpose repositories [below](#table-of-repositories).

General purpose repositories often have fairly large file size limits, can be used freely and provide API for programmatic access to data.

</div>

<div class='col-sm-6'>

<center><h5>Specialist Repositories></h5></center>
<center><i class='fas fa-briefcase fa-2x'></i></center>
Specialist repositories are designed for specific types of deposit, for instance; GIS, genomic, proteinomic, metereological or archeological data. Datasets require highly detailed meta-data to be added before they can be published, as users of these repositories expect to be able to filter or access datasets based on these fields. 

Scientific Data maintains an [excellent guide to specialist repositories](https://www.nature.com/sdata/policies/repositories) but you may wish to refer to [re3data.org](https://re3data.org) which is well regarded as the most exhaustive collection of (over 2,000) repositories. 

</div>

</div>

<hr>

It's important to note that your home institution may require that you update their institutional repository with a "meta data record" that contains the DOI for your research outputs, including deposits with data repositories. Contact your local research support teams for advice.

### **OxShef: dataviz** recommended repositories {#table-of-repositories}

```{r repositories-DT, echo = FALSE}
library("tidyverse")
library("DT")
library("readxl")

fa_scripting <- "<i class='fa fa-file-code fa-2x'></i>"
fa_pointAndClick <- "<i class='fa fa-hand-pointer fa-2x'></i>"

fa_icons <- tribble(
  ~tool.type, ~type,
  "Scripting", "<i class='fa fa-file-code fa-2x'></i>",
  "Point and Click", "<i class='fa fa-hand-pointer fa-2x'></i>"
)

oxshef_repositories <- read_xlsx("oxshef-repositories.xlsx")

oxshef_repositories %>%
  arrange(repository) %>%
  mutate(logo = paste0(
    "<a href='", url, "' target='_blank'>",
    "<img src='images/table-of-repositories-logos/", image.path, "' style='max-height:80px'></img>",
    "</a>"
  )) %>%
  # left_join(fa_icons) %>%
  # select(-url, -tool.type, -image.path, -tool) %>%
  # mutate(external.data.support = ifelse(external.data.support,
  #   "<i class='fas fa-circle'></i>",
  #   "<i class='far fa-circle'></i>"
  # )) %>%
  select(logo, everything(), -repository, -url, -image.path) %>%
  datatable(
    escape = FALSE,
    rownames = FALSE,
    colnames = c(
      "Repository",
      "Description",
      "DOI Versioning Info",
      "API info"
    ),
    options = list(
      scrollX = TRUE,
      autoWidth = TRUE,
      columnDefs = list(
        list(width = "100px", targets = c(0)),
        list(width = "400px", targets = c(1)),
        list(width = "250px", targets = c(2, 3)),
        list(className = "dt-center", targets = c(0))
      ),
      dom = "t"
    ),
    width = "100%"
  )
```